Gaussian mean estimation in simulated data sets

### 2018-09-29 analysis/gaussian.mean.est.Rmd
wflow_publish("gaussian.mean.est.Rmd")

*TO DO: Give overview of this report.*

@@

In this scenario, data sets are simulated using the "Spikes" mean
function and the "Clipped Blocks" variance function. This plot shows
the mean function as a block line, and the +/- 2 standard deviations
as orange lines:

@@

@@

In this scenario, we see that SMASH, allowing for heteroskedastic
errors, outperforms EbayesThresh and all variants of TI thresholding
(including TI thresholding with the true variance). Further, SMASH
performs almost as well when estimating the variance compared to when
provided with the true variance.

@@

In this next scenario, data sets are simulated using the "Corner" mean
function and the "Doppler" variance function. This plot shows the mean
function as a block line, and the +/- 2 standard deviations as orange
lines:

@@

Similar to the "spikes" data sets, we see that the SMASH method
allowing for heteroskedastic variances outperforms the TI thresholding
and EbayesThresh approaches.

>>>>

In this analysis, we assess the ability of different signal denoising
methods to recover the true signal after being provided with
Gaussian-distributed observations of the signal. We consider scenarios
in which the data have homoskedastic errors (constant variance) and
heteroskedastic errors (non-constant variance).

Since the simulation experiments are very computationally intensive,
they are implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

@@

In this scenario, data sets were simulated using the "Spikes" mean
function and the "Clipped Blocks" variance function. The next couple
plots reproduce part of Fig. 3 in the manuscript.

This plot shows the mean function as a block line, and the +/- 2
standard deviations as orange lines:

@@

Extract the results from running the simulations.

@@

In the "Spikes" scenario, we see that SMASH, when allowing for
heteroskedastic errors, outperforms EbayesThresh and all variants of
TI thresholding (including TI thresholding with the true variance).
Further, SMASH performs almost as well when estimating the variance
compared to when provided with the true variance.

@@

In this next scenario, the data sets were simulated using the "Corner"
mean function and the "Doppler" variance function. These plots were
also used for Fig. 3 of the manuscript.

This plot shows the mean function as a block line, and the +/- 2
standard deviations as orange lines:

@@

Similar to the "Spikes" scenario, we see that the SMASH method, when
allowing for heteroskedastic variances, outperforms both the TI
thresholding and EbayesThresh approaches.
